State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources

### 2021-02-23 analysis/paper/paper.Rmd
added some transparent elements to one plot

# color version
ts_col = plot_df %>%
  ggplot(aes(x = Start_Date)) +
  geom_ribbon(aes(ymin = trap_lowCI,
                  ymax = trap_uppCI,
                  fill = "Trap Est."),
              alpha = 0.4) +
  geom_ribbon(aes(ymin = `2.5%`,
                  ymax = `97.5%`,
                  fill = "Model"),
              alpha = 0.4) +
  geom_point(aes(y = win_cnt,
                 shape = 'Window Count',
                 color = 'Window Count'),
             size = pt_size) +
  geom_point(aes(y = trap_est,
                 shape = 'Trap Est.',
                 color = 'Trap Est.'),
             size = pt_size) +
  geom_line(aes(y = `50%`,
                color = 'Model')) +
  geom_point(aes(y = `50%`,
                 shape = 'Model',
                 color = 'Model'),
             size = pt_size) +
  scale_color_manual(values = c('Model' = 'black',
                                'Window Count' = 'blue',
                                'Trap Est.' = 'red'),
                     name = "Source") +
  scale_fill_manual(values = c('Model' = 'black',
                                'Window Count' = 'blue',
                                'Trap Est.' = 'red'),
                     guide = "none") +
  scale_shape_manual(values = c("Model" = 18,
                                "Window Count" = 1,
                                "Trap Est." = 8),
                     name = "Source") +
  theme_pubr(legend = "bottom") +
  facet_wrap(~ plot_title,
             scales = "free",
             ncol = 2) +
  labs(x = 'Date',
       y = 'Total Escapement (x 10,000)')

>>>>

# color version
ts_col = plot_df %>%
  ggplot(aes(x = Start_Date)) +
  geom_ribbon(aes(ymin = trap_lowCI,
                  ymax = trap_uppCI,
                  fill = "Trap Est."),
              alpha = 0.4) +
  geom_ribbon(aes(ymin = `2.5%`,
                  ymax = `97.5%`,
                  fill = "Model"),
              alpha = 0.4) +
  geom_point(aes(y = win_cnt,
                 shape = 'Window Count',
                 color = 'Window Count'),
             size = pt_size) +
  geom_point(aes(y = trap_est,
                 shape = 'Trap Est.',
                 color = 'Trap Est.'),
             size = pt_size) +
  geom_line(aes(y = `50%`,
                color = 'Model')) +
  geom_point(aes(y = `50%`,
                 shape = 'Model',
                 color = 'Model'),
             size = pt_size) +
  scale_color_manual(values = c('Model' = 'black',
                                'Window Count' = 'blue',
                                'Trap Est.' = 'red'),
                     name = "Source") +
  scale_fill_manual(values = c('Model' = 'black',
                                'Window Count' = 'blue',
                                'Trap Est.' = 'red'),
                     guide = "none") +
  scale_shape_manual(values = c("Model" = 18,
                                "Window Count" = 1,
                                "Trap Est." = 8),
                     name = "Source") +
  theme_pubr(legend = "bottom") +
  theme(panel.background = element_rect(color = "transparent"),
        plot.background = element_rect(color = "transparent"),
        legend.background = element_rect(color = "transparent")) +
  facet_wrap(~ plot_title,
             scales = "free",
             ncol = 2) +
  labs(x = 'Date',
       y = 'Total Escapement (x 10,000)')
